ARGoS-Blockchain interface

### 2020-08-25 article.tex
upd

Several recent works have addressed the combination of blockchain
technology and swarm robotics. This combinatin proves useful for
security, consensus finding, robot economies, robot-as-a-service, and
potentially many more.

However, running these experiments requires a suitable framework. Such
a framework proves useful both for researchers who do not have access
to a suitable robot platform, such as the Pi-puck robot. Additionally,
a suitable platform is important before running time- and
cost-consuming experiments with real robots.

The ARGoS robot simulator \citep{PinTriOGr-etal2012:si} is the
state-of-the-art research platform to conduct simulations in swarm
robotics.

In general, in swarm robotics research, each robot is a blockchain
node, and contributes to the maintenance of the system by exchanges
blockchain information. To link ARGoS and blockchain software, we
developed the ARGoS-Blockchain interface that provides access to the
blockchain nodes for the robots (Figure~\ref{fig:interface}). The
interface is intended to facilitate research in blockchain-based robot
swarms by allowing to call blockchain functions in
ARGoS. Additionally, Docker makes it easy to install and run the
interface on different platforms.

@@

%The Blockchain module is available at
%\url{https://github.com/Pold87/ARGoS-Blockchain-interface} and the
%ARGoS module is available at
%\url{https://github.com/Pold87/ARGoS-Blockchain-interface}.

%\dirtree{%
%.1 geth/.
%.1 img/.
%.1 local_scripts/.
%.1 .gitignore.
%.1 README.
%.1 docker-compose.yml.
%}

% TODO: this is a good figure, also include it
% \begin{figure}
%   \centering
%     \includegraphics[width=\textwidth]{Figure5}
%   \caption{For each robot, the ARGoS-Blockchain interface establishes
%     a connection to the Ethereum blockchain via a Docker container and
%     shell scripts that provide templates for executing Ethereum (geth)
%     functions.}
%   \label{fig:interface}  
% \end{figure}

@@

The very first time you run this code, it is required to create the
Docker image for the Ethereum nodes and initialize Docker Swarm as
follows:

\begin{verbatim}
cd geth/
docker build -t mygeth .
docker swarm init
\end{verbatim}

Additionally, you have to set the variable \verb|DOCKERFOLDER| in the
file \verb|global_config.sh| to the full path where this repository is
located on your computer, for example:

\begin{verbatim}
/Users/vstrobel/Documents/ARGoS-Blockchain-interface/
\end{verbatim}

@@

%\bibliographystyle{splncs04}
\bibliography{library}

>>>>

Several recent works have addressed the combination of blockchain
technology and swarm robotics
\cite{StrCasDor2018:aamas,StrDor2018:ants,StrFerDor2017:techreport-013}. This
combination proves useful for security, consensus finding, robot
economies, robot-as-a-service, and potentially many other applications
in robot swarms. However, conducting experiments involving robot
swarms and blockchain technology requires a suitable testbed. A widely
used framework consists of the Pi-puck robot platform running the
Ethereum blockchain network. However, not every researcher has access
to physical robots, obtaining and maintaining them be both
time-intense and cost-intense, not to mention the lengthy execution of
experiments. Therefore, a simulation testbed is needed to quickly try
and test different controllers and scenarios. The ARGoS robot
simulator \citep{PinTriOGr-etal2012:si} is the state-of-the-art
research platform to conduct simulations in swarm robotics. Such a
framework proves useful both for researchers who do not have access to
a suitable robot platform, such as the Pi-puck robot. Additionally, a
suitable platform is important before running time- and cost-consuming
experiments with real robots.

In general, in swarm robotics research, each robot is a blockchain
node, and contributes to the maintenance of the system by exchanges
blockchain information. To link ARGoS and blockchain software, we
developed the ARGoS-Blockchain interface that provides access to the
blockchain nodes for the robots (Figure~\ref{fig:interface}). The
interface is intended to facilitate research in blockchain-based robot
swarms by allowing to call blockchain functions in
ARGoS. Additionally, using Docker makes it easy to install and run the
interface on different platforms.

@@

The open-source software is available at GitHub: the blockchain module
is available at
\footnote{\url{https://github.com/Pold87/ARGoS-Blockchain-interface}}
and the ARGoS module is available at
\footnote{\url{https://github.com/Pold87/robot-swarms-need-blockchain}}.

\begin{figure}[t]%\centering
\dirtree{%
.1 geth/.
.1 img/.
.1 local\_scripts/.
.1 .gitignore.
.1 README.
.1 docker-compose.yml.
}
\label{fig:folderstructure}  
\caption{The folder structure of the package.}
\end{figure}
\begin{figure}
  \centering
    \includegraphics[width=\textwidth]{overview}
  \caption{For each robot, the ARGoS-Blockchain interface establishes
    a connection to the Ethereum blockchain via a Docker container and
    shell scripts that provide templates for executing Ethereum (geth)
    functions.}
  \label{fig:overview}  
\end{figure}

@@

\subsection{Requirements}
\begin{itemize}
\item Linux
\item Docker
\end{itemize}

\subsection{Installation: Blockchain module}
The very first time you run this code, it is required to create the
Docker image for the Ethereum nodes and initialize Docker Swarm as
follows:

\begin{verbatim}
git clone https://github.com/Pold87/ARGoS-Blockchain-interface
cd ARGoS-Blockchain-interface/ && cd geth/
sudo docker build -t mygeth .
sudo docker swarm init
\end{verbatim}

\subsection{Installation: ARGoS module}

\begin{verbatim}
git clone https://github.com/Pold87/robot-swarms-need-blockchain
cd robot-swarms-need-blockchain/
mkdir cmake/
cd cmake/
cmake ..
make
\end{verbatim}

Additionally, you have to set the variable \verb|DOCKERBASE| in the
file \verb|global_config.sh| to the full path where this repository is
located on your computer, for example:

\begin{verbatim}
DOCKERBASE='/home/vstrobel/Documents/docker-geth-network/'
\end{verbatim}

@@

\bibliographystyle{plain}
\bibliography{library}
